Another paper with lots of text and fancy pictures

### 2023-09-27 paper.tex
CFs of real examples

\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{bm}
\usepackage{xcolor}
\usepackage{algpseudocode}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{hyperref}
\usepackage{cleveref}

@@

\textcolor{red}{What about $C_3$?}

@@

\section{Results}
In this section we compute correlation functions for some real samples. Table
\ref{tab:summary} contains information about these samples.
\begin{table}[!htp]
  \centering
  \begin{tabular}{|c|c|c|c|c|}
    \hline
    Sample name & Image type & Dimensions (pixels) & Image resolution ($\mu m$) & $C_{0.5}$\\
    \hline
    Ceramic 1   & XCT & $500 \times 500 \times 500$ & 2.25 & 0.9823 \\
    Ceramic 2   & XCT & $500 \times 500 \times 500$ & 2.25 & 0.9890 \\
    Ceramic 3   & XCT & $500 \times 500 \times 500$ & 2.25 & 0.9712 \\
    Sandstone 1 & SEM &  $1280 \times 869$ & 0.10 & 0.9703 \\
    Sandstone 2 & SEM &  $1280 \times 869$ & 0.05 & 0.9897 \\
    Carbonate 1 & SEM &  $1024 \times 691$ & 0.06 & 0.9721 \\
    \hline
  \end{tabular}
  \caption{Summary of samples used for calculation of correlation functions.}
  \label{tab:summary}
\end{table}

>>>>

\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{bm}
\usepackage{xcolor}
\usepackage{algpseudocode}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{hyperref}
\usepackage{cleveref}
\usepackage[export]{adjustbox}

@@

@@

\section{Results}
In this section we compute correlation functions along the plane $XY$ for some
real samples, namely one three-dimensional XCT and one two-dimensional SEM
sample. Table \ref{tab:summary} contains information about these samples. Images
of the samples are on \cref{fig:samples}. On the plots of correlation functions
we provide a family of curves with the first argument of the correlation
function being fixed.

Correlation functions for the XCT sample are on
\cref{fig:sample-limestone-cf}. The plot of $S_3$ function allows us to estimate
porosity of the sample to be $\sim 0.04$ (note, that the curve with $r_1 = 0$ is
actually $S_2$ function). The two-point correlation function reaches plateau at
$r_2 \approx 200\div 225\ \mu m$ which means that two events of finding two
points in the void phase are independent if the points are farther than
$225\ \mu m$ from each other. We see that the sample is a little bit anisotropic
($S_3(0, 225) \approx S_3(150, 0)$). From analysis of $C_3$ function it can be
stated that the sample has clusters of void phase which are $\sim 200\ \mu m$ in
diameter.

Correlation functions for the SEM sample are on
\cref{fig:sample-sandstone-cf}. Porosity of the sample is $\sim 0.3$ as follows
from the plot of $S_3$ function at $r_1 = 0$. The funcion $S_3(0, r_2)$ reaches
plateau at $r_2 \approx 20\ \mu m$. The sample is highly anisotropic (elongated
along the ordinate). The samples has clusters which are $\sim 45\ \mu m$ in
diameter.
\begin{table}[!htp]
  \centering
  \begin{tabular}{|c|c|c|c|c|}
    \hline
    Sample name & Image type & Dimensions (pixels) & Image resolution ($\mu m$) & $C_{0.5}$\\
    \hline
    Limestone & XCT &  $600 \times 600 \times 600$ & 3.02 & 0.9712 \\
    Sandstone & SEM &  $1280 \times 869$ & 0.10 & 0.9703 \\
    \hline
  \end{tabular}
  \caption{Summary of samples used for calculation of correlation functions.}
  \label{tab:summary}
\end{table}

\begin{figure*}[tp]
  \centering
  \subfigure[Limestone]{
    \includegraphics[width=0.45\linewidth]{images/carb.png}
    \label{fig:sample-limestone}}
  \hfill
  \subfigure[Sandstone (different clusters of void phase are shown in color)]{
    \includegraphics[width=0.45\linewidth, frame]{images/sandstone1.png}
    \label{fig:sample-sandstone}}
  \caption[]{Images of samples used for calculation of higher-order correlation
    functions.}
  \label{fig:samples}
\end{figure*}

\begin{figure}[tp]
  \centering
  \includegraphics[width=0.3\linewidth]{images/carb.npy-surf3.png}
  \hfill
  \includegraphics[width=0.3\linewidth]{images/carb.npy-surf2void.png}
  \hfill
  \includegraphics[width=0.3\linewidth]{images/carb.npy-surfvoid2.png}
  \vskip\baselineskip
  \includegraphics[width=0.3\linewidth]{images/carb.npy-s3.png}
  \includegraphics[width=0.3\linewidth]{images/carb.npy-c3.png}
  \caption[]{Correlation functions for carbonate sample
    (\cref{fig:sample-limestone}).}
  \label{fig:sample-limestone-cf}
\end{figure}

\begin{figure}[tp]
  \centering
  \includegraphics[width=0.45\linewidth]{images/sandstone1.png-surf2void.png}
  \hfill
  \includegraphics[width=0.45\linewidth]{images/sandstone1.png-surfvoid2.png}
  \vskip\baselineskip
  \includegraphics[width=0.45\linewidth]{images/sandstone1.png-s3.png}
  \hfill
  \includegraphics[width=0.45\linewidth]{images/sandstone1.png-c3.png}
  \caption[]{Correlation functions for sandstone sample
    (\cref{fig:sample-sandstone}).}
  \label{fig:sample-sandstone-cf}
\end{figure}
